Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-30 paper/src/paper.tex
modif artifact

\usepackage{listings}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[scientific-notation=true]{siunitx}

@@

\bigskip
The management generates a huge amount of data.
During the last few years, there was an explosion of the number of works 
at the interface of HPC and BigData, dealing with learning algorithms
(including the authors of this work~\cite{SC2015}).
Most of these studies target the process of determining more or less 
accurately the value of some specific key parameters, with the idea that
learning better estimates should improve the performances of the 
resource manager.

@@

In order to simulate how the simulation strategy for selecting policies would work on non simulated traces, we randomly introduce noise in the estimate of the waiting time defined by Eq.~\ref{eq:cost-exact} by rescaling, either dow or up, the waiting time of jobs obtained by simulation:
%
\begin{equation}
\label{eq:cost-exact}
w_{\mbox{noisy}}(t;P_i) = \sum_{j=1}^{l(\Delta_t)} \rho \mbox{Wait}_j^{P_i}
\end{equation}
%

@@

Authors are sorted in alphabetical order. The authors would like to warmly
thank Pierre Neyron for help with computational experiments and Arnaud Legrand
for discussions about reproducibility. We gracefully thank the contributors of
the Parallel Workloads Archive, Victor Hazlewood (SDSC SP2), Travis Earheart
and Nancy Wilkins-Diehr (SDSC Blue), Lars Malinowsky (KTH SP2), Dan Dwyer and
Steve Hotovy (CTC SP2), Joseph Emeras (CEA Curie and UniLu Gaia), Susan
Coghlan, Narayan Desay, Wei Tang (ANL Intrepid), and of course Dror Feitelson.
The Metacentrum workload log was graciously provided by the Czech National Grid
Infrastructure MetaCentrum. This work has been partially supported by the LabEx
PERSYVAL-Lab(\grantsponsor{ANR-11-LABX-0025-01}{ANR-11-LABX-0025-01}) funded by
the French program Investissement d'avenir. Experiments presented in this paper
were carried out using the Grid'5000 testbed. Grid'5000 is supported by a
scientific interest group hosted by Inria and including CNRS, RENATER and
several Universities as well as other
organizations\footnote{https://www.grid5000.fr}.  Access to the experimental
machine(s) used in this paper was gracefully granted by research teams from
LIG\footnote{http://www.liglab.fr} and Inria\footnote{http://www.inria.fr}.

\end{acks}

@@

this appendix describes the computational artifacts associated with this work. we
take a lightweight approach to replicability by packaging a declarative
workflow that generates all the figures from this paper and making it available
publicly. moreover, questions regarding replication can be freely directed at
the authors via e-mail.

all the code associated with this work is released under the ~\cite{isc}
license as a persistent zenodo~\cite{zenodo} archive at~\cite{zenodomain}.

@@

There are various approaches for making computational experiments replicable,
among which distributing complete operating system images, containers, or
packaging software. as our experiments are cpu bound, we decide to opt for the
software packaging approach using the nix~\cite{nix} packaging system. This
allows for replicating the experiments on clusters where virtualization is not
available or kernels are old and decreases runtime. all the dependencies of our
experiments (including our own code, dependencies for data processing and
visualization and workflow engine) are automatically managed by Nix up to the
actual execution of the code.

\subsubsection{check-list (artifact meta information)}

@@

@@

Managed by Nix.

>>>>

\usepackage{listings}
\usepackage{dirtree}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[scientific-notation=true]{siunitx}

@@

\bigskip
The management generates a huge amount of data.
During the last few years, there was an explosion of the number of works
at the interface of HPC and BigData, dealing with learning algorithms
(including the authors of this work~\cite{learningruntimes}).
Most of these studies target the process of determining more or less
accurately the value of some specific key parameters, with the idea that
learning better estimates should improve the performances of the
resource manager.

@@

In order to simulate how the simulation strategy for selecting policies would work on non simulated traces, we randomly introduce noise in the estimate of the waiting time defined by Eq.~\ref{eq:cost-exact} by rescaling, either dow or up, the waiting time of jobs obtained by simulation:
%
\begin{equation}
\label{eq:cost-noisy}
w_{\mbox{noisy}}(t;P_i) = \sum_{j=1}^{l(\Delta_t)} \rho \mbox{Wait}_j^{P_i}
\end{equation}
%

@@

Authors are sorted in alphabetical order. The authors would like to warmly
thank Pierre Neyron for help with computational experiments and Arnaud Legrand
for discussions about reproducibility. We gracefully thank the contributors of
the Parallel Workloads Archive, Victor Hazlewood (SDSC SP2), Travis Earheart
and Nancy Wilkins-Diehr (SDSC Blue), Lars Malinowsky (KTH SP2), Dan Dwyer and
Steve Hotovy (CTC SP2), Joseph Emeras (CEA Curie and UniLu Gaia), Susan
Coghlan, Narayan Desay, Wei Tang (ANL Intrepid), and of course Dror Feitelson.
The Metacentrum workload log was graciously provided by the Czech National Grid
Infrastructure MetaCentrum. This work has been partially supported by the LabEx
PERSYVAL-Lab(\grantsponsor{ANR-11-LABX-0025-01}{ANR-11-LABX-0025-01}) funded by
the French program Investissement d'avenir.
\end{acks}

@@

This appendix describes the computational artifacts associated with this work. We
take a lightweight approach to replicability by packaging a declarative
workflow that generates all the figures from this paper and making it available
publicly. Moreover, questions regarding replication can be freely directed at
the authors via e-mail.

All the code associated with this work is released under the ~\cite{isc}
license as a persistent zenodo~\cite{zenodo} archive at~\cite{zenodomain}.

@@

There are various approaches for making computational experiments replicable,
among which distributing complete operating system images, containers, or
packaging software. As our experiments are cpu bound, we decide to opt for the
software packaging approach. This allows for replicating the experiments on clusters where virtualization is not
available or kernels are too old for containers old and decreases runtime.

All the dependencies of our
experiments (including our own code, dependencies for data processing and
visualization and workflow engine) are automatically managed by Nix up to the
actual execution of the code.

\subsubsection{Check-list (artifact meta information)}

@@

 Experiments presented in this paper were carried out using the Grid'5000
 testbed. Grid'5000 is supported by a scientific interest group hosted by Inria
 and including CNRS, RENATER and several Universities as well as other
 organizations\footnote{https://www.grid5000.fr}.  Access to the experimental
 machine(s) used in this paper was gracefully granted by research teams from
 LIG\footnote{http://www.liglab.fr} and Inria\footnote{http://www.inria.fr}.

@@

All the software dependencies of our code
Managed by Nix.

\dirtree{%
.1 root .
.2 zymakefile .
.2 default.nix .
.2 pkgs .
.2 gz .
.3 ANL-Intrepid.swf.gz .
.3 CEA-Curie.swf.gz .
.3 CTC-SP2.swf.gz .
.3 KTH-SP2.swf.gz .
.3 SDSC-BLUE.swf.gz .
.3 SDSC-SP2.swf.gz .
.3 UniLu-Gaia.swf.gz .
.2 misc .
.3 strongvisu .
.3 visu .
.2 ocst .
.2 paper .
}
